\class : Problem Set \psetnum

### 2022-04-12 531_stars/pset2/solutions.tex
stars pset2 q4

>>>>

\question{\textbf{9.2 - Hey, where'd the sun go!?}}
\answer{
    If the sun were to suddenly stop nuclear fusion then how it would take us to realise would depend on what we were measuring. If we happen to have a fancy neutrino detector then the answer would be the photon travel time since the neutrinos would immediately stop appearing - I feel as though people would probably assume instrumental errors rather than the sun giving up on fusion though ;)

    Assuming we're just using good old EM detectors, then I think the answer is instead the \textbf{dynamical timescale}. We can immediately rule out the nuclear timescale since that's only relevant with nuclear fuel running out (rather than being arbitrarily cut off as in this case). One may argue for the thermal timescale, since this is how long it would actually take for the Sun's luminosity to reflect its lack of internal energy production. However, upon the removal of the central energy source, the sun would start to contract on the dynamical timescale to remain in hydrostatic equilibrium and thus we could measure this contraction and notice the sun has broken in this time (about an hour for the sun).
}
